04-Data-Analysis

### 2021-04-22 00-Data-Processing/04-Data-Analysis.Rmd
Update 04-Data-Analysis.Rmd
Removed some comments and duplicate code

Join the household data to the travel time matrices:
```{r}
ttm_car <- ttm_car %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            income_less40k,
                            DAUID, 
                            TAZUID),
            by = c("UID" = "ID"))

ttm_transit <- ttm_transit %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            income_less40k,
                            DAUID, 
                            TAZUID),
            by = c("UID" = "ID"))

ttm_walk <- ttm_walk %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            income_less40k,
                            DAUID, 
                            TAZUID),
            by = c("UID" = "ID"))
```

@@

Prepare and join population data:
```{r number-of-residential-units-per-DA, include=FALSE}
# Data preparation
## Find number of residential units in each DA. This is needed to assign the population to parcels
residential_units <- dwelling_network_points_2016 %>%
  st_drop_geometry() %>%
  group_by(TAZUID) %>%
  summarize(residential_units = sum(Dwellings))
```

```{r join-population-data-to-travel-time-tables, include=FALSE}
# Data preparation
## Join the population data to the travel time matrices:
ttm_car <- ttm_car %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::transmute(ID, 
                            children,
                            adults,
                            seniors),
            by = c("UID" = "ID"))

ttm_transit <- ttm_transit %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::transmute(ID, 
                            children,
                            adults,
                            seniors),
            by = c("UID" = "ID"))

ttm_walk <- ttm_walk %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::transmute(ID, 
                            children,
                            adults,
                            seniors),
            by = c("UID" = "ID"))
```

Join all tables:
```{r}
ttm <- ttm_car %>%
  rename(travel_time_car = travel_time) %>%
  full_join(ttm_transit %>%
              transmute(UID,
                        OBJECTID,
                        travel_time_transit = travel_time),
            by = c("UID", "OBJECTID")) %>%
  full_join(ttm_walk %>%
              transmute(UID,
                        OBJECTID,
                        travel_time_walk = travel_time),
            by = c("UID", "OBJECTID"))
```

@@

Quartiles of accessibility:
```{r}
# acc_quintiles_pre <- quantile(accessibility %>%
#                                 filter(timing == "Pre-covid") %>%
#                                 pull(accessibility),
#                               c(0, 0.25, 0.5, 0.75, 1))
# acc_quintiles_covid <- quantile(accessibility %>%
#                                 filter(timing == "During covid") %>%
#                                 pull(accessibility),
#                               c(0, 0.25, 0.5, 0.75, 1))
```

Quartiles of accessibility change:
```{r}
acc_quintiles_change <- quantile(accessibilty_change$acc_d,
                              c(0, 0.25, 0.5, 0.75, 1))
```

Add labels of accessibility levels to table:
```{r}
# accessibility <- accessibility %>%
#   mutate(accessibility_level = case_when(timing == "Pre-covid" & accessibility <= acc_quintiles_pre[2] ~ "Bottom 25%",
#                                          timing == "Pre-covid" & accessibility > acc_quintiles_pre[2] & accessibility <= acc_quintiles_pre[3] ~ "Third 25%",
#                                          timing == "Pre-covid" & accessibility > acc_quintiles_pre[3] & accessibility <= acc_quintiles_pre[4] ~ "Second 25%",
#                                          timing == "Pre-covid" & accessibility > acc_quintiles_pre[4] ~ "Top 25%",
#                                          timing == "During covid" & accessibility <= acc_quintiles_covid[2] ~ "Bottom 25%",
#                                          timing == "During covid" & accessibility > acc_quintiles_covid[2] & accessibility <= acc_quintiles_covid[3] ~ "Third 25%",
#                                          timing == "During covid" & accessibility > acc_quintiles_covid[3] & accessibility <= acc_quintiles_covid[4] ~ "Second 25%",
#                                          timing == "During covid" & accessibility > acc_quintiles_covid[4] ~ "Top 25%"),
#            accessibility_level = factor(accessibility_level,
#                                         levels = c("Top 25%", "Second 25%", "Third 25%", "Bottom 25%"),
#                                         ordered = TRUE))
```

>>>>

Prepare and join population data from TTS:
```{r number-of-residential-units-per-DA, include=FALSE}
# Data preparation
## Find number of residential units in each DA. This is needed to assign the population to parcels
residential_units <- dwelling_network_points_2016 %>%
  st_drop_geometry() %>%
  group_by(TAZUID) %>%
  summarize(residential_units = sum(Dwellings))
```

Join the household data to the travel time matrices:
```{r}
ttm_car <- ttm_car %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            income_less40k,
                            children,
                            adults,
                            seniors,
                            DAUID, 
                            TAZUID),
            by = c("UID" = "ID"))

ttm_transit <- ttm_transit %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            income_less40k,
                            children,
                            adults,
                            seniors,
                            DAUID, 
                            TAZUID),
            by = c("UID" = "ID"))

ttm_walk <- ttm_walk %>%
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              dplyr::select(ID, 
                            income_less40k,
                            children,
                            adults,
                            seniors,
                            DAUID, 
                            TAZUID),
            by = c("UID" = "ID"))
```

@@

### Join Tables into Single TTM
Join all tables:
```{r}
ttm <- ttm_car %>%
  rename(travel_time_car = travel_time) %>%
  full_join(ttm_transit %>%
              transmute(UID,
                        OBJECTID,
                        travel_time_transit = travel_time),
            by = c("UID", "OBJECTID")) %>%
  full_join(ttm_walk %>%
              transmute(UID,
                        OBJECTID,
                        travel_time_walk = travel_time),
            by = c("UID", "OBJECTID"))
```

@@

Quartiles of accessibility:
```{r}
 acc_quintiles_pre <- quantile(accessibility %>%
                                 filter(timing == "Pre-covid") %>%
                                 pull(accessibility),
                               c(0, 0.25, 0.5, 0.75, 1))
 acc_quintiles_covid <- quantile(accessibility %>%
                                 filter(timing == "During covid") %>%
                                 pull(accessibility),
                               c(0, 0.25, 0.5, 0.75, 1))
```

Quartiles of accessibility change:
```{r}
acc_quintiles_change <- quantile(accessibility_change$acc_d,
                              c(0, 0.25, 0.5, 0.75, 1))
```

Add labels of accessibility levels to table:
```{r}
 accessibility <- accessibility %>%
   mutate(accessibility_level = case_when(timing == "Pre-covid" & accessibility <= acc_quintiles_pre[2] ~ "Bottom 25%",
                                          timing == "Pre-covid" & accessibility > acc_quintiles_pre[2] & accessibility <= acc_quintiles_pre[3] ~ "Third 25%",
                                          timing == "Pre-covid" & accessibility > acc_quintiles_pre[3] & accessibility <= acc_quintiles_pre[4] ~ "Second 25%",
                                          timing == "Pre-covid" & accessibility > acc_quintiles_pre[4] ~ "Top 25%",
                                          timing == "During covid" & accessibility <= acc_quintiles_covid[2] ~ "Bottom 25%",
                                          timing == "During covid" & accessibility > acc_quintiles_covid[2] & accessibility <= acc_quintiles_covid[3] ~ "Third 25%",
                                          timing == "During covid" & accessibility > acc_quintiles_covid[3] & accessibility <= acc_quintiles_covid[4] ~ "Second 25%",
                                          timing == "During covid" & accessibility > acc_quintiles_covid[4] ~ "Top 25%"),
            accessibility_level = factor(accessibility_level,
                                         levels = c("Top 25%", "Second 25%", "Third 25%", "Bottom 25%"),
                                         ordered = TRUE))
```
